Explore tumor cell classification with CellAssign

### 2024-05-30 analyses/cell-type-ewings/template_notebooks/02-cellassign.Rmd
account for only one cell type and skip confusion matrix

```{r, eval=has_tumor_assignments}
# prep annotations for confusion matrix
celltype_df <- celltype_df |> 
  dplyr::mutate(cellassign_annotations = ifelse(
    # make sure annotations match marker gene annotations
    cellassign_annotations == "tumor", "Tumor", "Normal"
  )) |> 
  # make tumor the positive class
  dplyr::mutate(
    cellassign_annotations = forcats::fct_relevel(cellassign_annotations, "Tumor"),
    marker_gene_classification = forcats::fct_relevel(marker_gene_classification, "Tumor")
  )

caret::confusionMatrix(
  table(
    celltype_df$marker_gene_classification, 
    celltype_df$cellassign_annotations)
)
```

>>>>

```{r, eval=has_tumor_assignments}
# make sure that we only run if both classes are found in both cell types 
if(all(c("other", "tumor") %in% celltype_df$cellassign_annotations) &&
   all(c("Tumor", "Normal") %in% celltype_df$marker_gene_classification)){
  # prep annotations for confusion matrix
  celltype_df <- celltype_df |> 
    dplyr::mutate(cellassign_annotations = ifelse(
      # make sure annotations match marker gene annotations
      cellassign_annotations == "tumor", "Tumor", "Normal"
    )) |> 
    # make tumor the positive class
    dplyr::mutate(
      cellassign_annotations = forcats::fct_relevel(cellassign_annotations, "Tumor"),
      marker_gene_classification = forcats::fct_relevel(marker_gene_classification, "Tumor")
    )

  caret::confusionMatrix(
    table(
      celltype_df$marker_gene_classification, 
      celltype_df$cellassign_annotations)
  ) 
}
```
